\vspace{-2cm} Content of Municipal Government Websites

### 2017-02-23 paper/manuscript.tex
improved file type and size tables

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Feb 22 14:08:54 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{rr}
		\hline
		& V1 \\
		\hline
		.asp &   1 \\
		.aspx &  43 \\
		.css &  32 \\
		.doc &  35 \\
		.docx &   5 \\
		.eot &   1 \\
		.gif &  99 \\
		.GIF &   1 \\
		.htm &   2 \\
		.html & 819 \\
		.ico &   1 \\
		.jpg & 131 \\
		.JPG &  26 \\
		.js &  51 \\
		.Net &  12 \\
		.pdf & 1371 \\
		.PDF &  50 \\
		.png & 210 \\
		.PNG &   1 \\
		.ppt &   1 \\
		.swf &   1 \\
		.ttf &   3 \\
		.txt &   1 \\
		.woff &   2 \\
		.xls &   2 \\
		.xlsx &   6 \\
		.xml &   3 \\
		\hline
	\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Feb 22 21:39:50 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lr}
		\hline
		File type & Occurrences \\ 
		\hline
		.pdf & 1371 \\ 
		.html & 819 \\ 
		.png & 210 \\ 
		.jpg & 131 \\ 
		.gif &  99 \\ 
		.js &  51 \\ 
		.PDF &  50 \\ 
		.aspx &  43 \\ 
		.doc &  35 \\ 
		.css &  32 \\ 
		.JPG &  26 \\ 
		.Net &  12 \\ 
		.xlsx &   6 \\ 
		.docx &   5 \\ 
		.ttf &   3 \\ 
		.xml &   3 \\ 
		.htm &   2 \\ 
		.woff &   2 \\ 
		.xls &   2 \\ 
		.asp &   1 \\ 
		.eot &   1 \\ 
		.GIF &   1 \\ 
		.ico &   1 \\ 
		.PNG &   1 \\ 
		.ppt &   1 \\ 
		.swf &   1 \\ 
		.txt &   1 \\ 
		\hline
	\end{tabular}
	\caption{File types in scraped websites} 
\end{table}

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Feb 22 21:35:10 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lrr}
		\hline
		Website & Files & Size (MB) \\ 
		\hline
		brownsvilletn.gov & 188 & 14328 \\ 
		www.centralpointoregon.gov & 150 & 137440 \\ 
		www.dedham-ma.gov & 603 & 212572 \\ 
		www.duncanok.gov &  84 & 47064 \\ 
		www.dutchessny.gov & 110 & 291376 \\ 
		www.ennistx.gov & 200 & 26244 \\ 
		www.greenvillenc.gov & 333 & 25732 \\ 
		www.romi.gov & 491 & 112584 \\ 
		www.trumbull-ct.gov & 787 & 191540 \\ 
		www.westonct.gov & 861 & 213140 \\ 
		\hline
	\end{tabular}
	\caption{Test websites} 
\end{table}
